Stack Safety as a Security Property

### 2020-07-09 main.tex
Abstract

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
\bcp{Hey, we should have an abstract \ldots}
\end{abstract}

@@

Enforcement mechanisms are modeled as {\em policies} that add some auxiliary
policy state to the ordinary machine state\bcp{This may be surprising to
  people who are not thinking about micropolicies.\apt{added para below}} and a partial policy
step function that
refines the machine step function by allowing or disallowing a step to be taken
based on its auxiliary state. This model will be made more precise in
\cref{sec:prelim}. It is flexible enough to capture any kind of mechanism used
for dynamic enforcement of properties of interest, including the following
representative families of policies.

We model ordinary program state and policy enforcement state separately to make it 
easier to use well-established concepts from language-based security.  
In particular, confidentiality has an elegant extensional characterization in terms of
\emph{noninterference}: a program preserves the confidentiality of certain data if
\emph{varying} that data would not change the program's observable behavior~\cite{??}.
In applying this idea to a system that incorporates policy enforcement, only
ordinary program data should be varied, whereas any associated policy enforcement
state should be left alone; our model makes this distinction obvious.
%That is, we compare the actual execution of the program with a \emph{hypothetical}
%execution where data has been varied. 
We also introduce a notion of observational integrity that relies on the idea of
\emph{rolling back} program state; again, our model makes it easy to describe
rollback of ordinary program data while leaving policy enforcement data unchanged.

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  What is stack safety? While many mechanisms have been proposed to
  protect against attacks that influence the call stack of a program,
  and many others rely on a protected stack as an assumption to
  provide higher level guarantees, a clear stack safety definition
  is missing from the literature.
%
  In this paper we give such a formal definition of stack safety as a
  security property.
  %
  We also explore how this formal definition can be enforced by
  previously proposed security mechanisms and discuss provably
  stronger and weaker variations of interest.
\end{abstract}

@@

Enforcement mechanisms are modeled as {\em policies} that add some auxiliary
policy state to the ordinary machine state\bcp{This may be surprising to
  people who are not thinking about micropolicies.} and a partial policy
step function that
refines the machine step function by allowing or disallowing a step to be taken
based on its auxiliary state. This model will be made more precise in
\cref{sec:prelim}. It is flexible enough to capture any kind of mechanism used
for dynamic enforcement of properties of interest, including the following
representative families of policies.
